\documentclass[11pt,a4paper]{report}

% NOTE: packages used
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{xcolor}
\usepackage{xcolor, listings}
\usepackage{caption}

% NOTE: declarations and definitions document wide:
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\setlength{\parskip}{1.2ex}
\setlength{\parindent}{2em}

% dark green:
\definecolor{green2}{HTML}{347235}

\title{ServeD WebAPI - documentation - version 0.1.1}
\author{\href{mailto:dmilith@verknowsys.com}{Daniel (dmilith) Dettlaff}}
\date{2012-12-14}

% NOTE: document content:
\begin{document}
\maketitle


\section{HTTP JSON API Calls}\label{sec:apicalls}
  All calls are by default using HTTP POST method.

  \begin{itemize}

    \item \#001 - /GetUserProcesses - Gets process information from all services and applications running by user (owner of web panel).
      \begin{itemize}
        \item params: no additional params.
        \item return type: JSON.
        \item errors: {message: MESSAGE} where MESSAGE is one of error codes: KDERR, NOPCS.
        \item format: {message: MESSAGE, content: [{properties,…},…]}
      \end{itemize}

    \item \#002 - /RegisterDomain - Registers user domain.
      \begin{itemize}
        \item params: Accepts additional http param as domain, or takes \"RegisterDomain\" key from http body data array (when no additional http param is provided).
        \item return type: JSON
        \item format: {message: \"information\", content: [{properties,…},…]}
      \end{itemize}

  \end{itemize}


\section{HTTP JSON API Errors}\label{sec:apierrors}
  All errors should have only two fields with JSON object respond: "status" and "message".

  \begin{itemize}
    \item "message" contains detailed information about error.
    \item "status" codes:
      \begin{description}
        \item{0} - API Request executed successfully.
        \item{1} - Invalid API Request.
        \item{2} - Error executing API Request.
        \item{3} - API Request Timeout.
        \item{4} - API Request Crashed.
        \item{-2} - Native error: NOPCS.
        \item{-1} - Native error: KDERR.
      \end{description}

  \end{itemize}


\end{document}
